Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-11-02 manuscript/manuscript.tex
Added todonote in real data example

We must also define a density function for the entire model.
\citet{Sigismondi2012} proposed a minimum and a maximum density for the Neuqu\'en basin of 275kg/m$^3$ and 412kg/m$^3$, respectively.
So we have chosen, for this specific example, a linear density that assumes the minimum value on the surface and the maximum at 5858m, i.e. the bottom of the basin.

>>>>

We must also define a density function for the entire model.
\citet{Sigismondi2012} proposed a minimum and a maximum density for the Neuqu\'en basin of 275kg/m$^3$ and 412kg/m$^3$, respectively.\todo{ver que esos valores son de contraste y tienen q ir negativos. poner los valores absolutos.}
So we have chosen, for this specific example, a linear density that assumes the minimum value on the surface and the maximum at 5858m, i.e. the bottom of the basin.
